Logistic Regression and SVM

### 2019-11-11 simple_ml/example/report2/paper.tex
partial complete exp2.

%\usepackage{subfigure} % Written by Steven Douglas Cochran
                        % This package makes it easy to put subfigures
                        % in your figures. i.e., "figure 1a and 1b"
                        % Docs are in "Using Imported Graphics in LaTeX2e"
                        % by Keith Reckdahl which also documents the graphicx
                        % package (see above). subfigure.sty is already
                        % installed on most LaTeX systems. The latest version
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/subfigure/

@@

% Write abstract here
\begin{abstract}
In this report, we solve the binary classification problem in a9a dataset by Logistic Regression (LR) and Support Vector Machine (SVM). \\
We perform experiments on four aspects: \\
1. Loss function comparision in SVM. \\
2. Hyper-parameter tuning in SVM. \\
3. Initilizer comparision in both LR and SVM. \\
4. Optimizer comparision in both LR and SVM. \\
\end{abstract}

@@

% Main Part
\section{Methods and Theory}
In this part, we first define logistic regression and SVM. Then we define LR's loss function Binary Cross Entrophy (BCE) and SVM's loss function Hinge Loss (HL). Mean Squared Error (MES) loss function. Then we solve the closed form solution for LR and its variant RR. At last we define GD algorithm, and its variants SGD and MBGD.
\subsection{Logistic Regression}
Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in {0, 1}$. Mathematically, for a single training datapoint $(x, y)$, LR assumes: \par
 \begin{center}
	\begin{equation}
	P(Y = 1|X = x) = \sigma(z) 
	\end{equation}
	\begin{equation}
	P(Y = 0|X = x) = 1 - \sigma(z)
	\end{equation}
	\begin{equation}
	z = F(x; W)
	\end{equation}
\end{center} \par
where $F(x; W)$ is linear regression parameterized by $W$ and $\sigma(.)$ is sigmoid function, where $\sigma(z) = \frac{1}{1 + e^{-z}} \in (0, 1)$.
\subsection{Binary Cross Entrophy}
Logistic regression assume each datapoint is independent, so the likelihood of all data is: \par
\begin{equation}
	\begin{aligned}
	L(W) &= \prod_{i=1}^m P(Y = y_i | X = x_i) \\ &= \prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} )
	\end{aligned}
\end{equation} \par

So our goal is to maximize the likelihood of data, in practice we maximize the log likelihood. \par
\begin{equation}
\begin{aligned}
LL(W) &= log\prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} ) \\ &= \Sigma_{i=1}^{m} y_i \sigma(z) + (1 - y_i)(1 - \sigma(z))
\end{aligned}
\end{equation} \par

\subsection{Ridge Regression}
In Equation~\ref{eq:cfs}, when $n > m$, $X^{T}X$ is not invertible. Ridge Regression tackle this problem by adding a small term. So the CFS for RR is
\begin{equation}
W_{ridge}^{*} = (X^{T}X + \lambda \mathbf{I})^{-1}X^{T}y
\end{equation} \par
Where $\mathbf{I}$ is identity matrix. \par
In this way, the loss function for Ridge Regression is
\begin{equation}
L_{ridge}(\hat{y}, y) = \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)  + \frac{1}{2} W^{T} W
\end{equation} \par
In another point of view, RR can be seen as a regularized version of LR.
\subsection{Gradient Descent}
Not all problem can be derived a CFS, which is often the case in machine learning. So instead of getting the best parameters $W^{*}$ immedeatly, we can update it incremently until $W$ gets close enough to $W^{*}$. That is the basic idea of GD algorithm. GD algorithm can be found in Algorithm~\ref{alg: Gradient_Descent}. 
\begin{algorithm}

	\label{alg: Gradient_Descent}
	\caption{Gradient Descent}
	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
	\KwOut{Optimized parameter $\hat{W}$}
	$t \gets 1$ \\
	\For{$t < N $}
	{
		$\hat{y} \gets X^{T}W $ \\
		$ L(\hat{y}, y) \gets \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)$ \\
		$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
		$W \gets W - \eta * \Delta{W}$ \\
	}
	$\hat{W} \gets W$ \\
	return $\hat{W}$
\end{algorithm}

\subsection{Stochastic Gradient Descent}
Different from GD which updates after it computes the gradient of parameters over all examples, stochastic gradient descent updates immediately once it computes parameters' gradient from only one example. SGD algorithm can be found in Algorithm~\ref{alg: Stochastic_Gradient_Descent}. It can be seen in the algorithm that, there is another for loop inside the for loop of GD algorithm, which leads to time un-efficiency.
\begin{algorithm}
		\label{alg: Stochastic_Gradient_Descent}
	\caption{Stochastic Gradient Descent}
	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
	\KwOut{Optimized parameter $\hat{W}$}
	$t \gets 1$ \\
	\For{$t < N $}
	{
		$ i \gets 0 $ \\
		\For{$ i < m $}
		{
			$\hat{y}_{i} \gets X^{T}_{i}W $ \\
			$ L(\hat{y}_{i}, y_{i}) \gets \frac{1}{2}(\hat{y}_{i} - y_{i})^{T}(\hat{y}_{i} - y_{i})$ \\
			$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
			$W \gets W - \eta * \Delta{W}$ \\
		}
	}
	$\hat{W} \gets W$ \\
	return $\hat{W}$
\end{algorithm}

\subsection{Mini Batch Gradient Descent}
Due to the fact that SGD updates the parameters based on only one examples, which it is time-comsuming, mini batch gradient descent updates the parameter based on a batch of examples, typically the batch size is bigger than 1 and smaller than the number of whole examples, e.g. 8, 16, 32... MBGD Algorithm can be found in Algorithm~\ref{alg: Mini_Batch_Gradient_Descent}.
\begin{algorithm}
	\label{alg: Mini_Batch_Gradient_Descent}
	\caption{Mini Batch Gradient Descent}
	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
	\KwOut{Optimized parameter $\hat{W}$}
	$t \gets 1$ \\
	\For{$t < N $}
	{
		$ i \gets 0 $ \\
		\For{$ X_{batch}, y_{batch} $ in $D$}
		{
			$\hat{y}_{batch} \gets X^{T}_{batch}W $ \\
			$ L(\hat{y}_{batch}, y_{batch}) \gets \frac{1}{2}(\hat{y}_{batch} - y_{batch})^{T}(\hat{y}_{batch} - y_{batch})$ \\
			$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
			$W \gets W - \eta * \Delta{W}$ \\
		}
	}
	$\hat{W} \gets W$ \\
	return $\hat{W}$
\end{algorithm}

\section{Experiments}
\subsection{Dataset}
We conduct all the experiments on housing dataset, which has total 506 examples and each example's form is $(x, y)$, where $x \in \mathbf{R}^{13}$ and $y \in \mathbf{R}$. We split the dataset into three part: 272 training examples, 67 validation examples and 167 test examples. $X$ is already scaled between $-1$ and $1$. And we normalized the $X_{train}, X_{val}, X_{test} $ by using the mean and variance of $X_{train}$.

\subsection{Implementation}
We implement the LR, RR and GD, GD, MBGD algorithm using python and mainly rely on the numpy package.

\subsection{Linear Regression and Ridge Regression}
In this section, we conduct the experiment of serveral magnitude of $\lambda$ of RR in training set, which leads to serveral $W_{ridge}$. We use $L_2{norm}$ to represent the magnitude of a vector. Given $v \in \mathbf{R}^{n}$
\begin{equation}
	L_2norm(v) = \sqrt{\Sigma_{i=1}^{n} v_{i}}
\end{equation} \par
From Table~\ref{tab:Ridge_Regression}, we can see that: \par
First, as the magnitude of lambda becomes bigger, both $MSE_{train}$ and $MSE_{val}$ become bigger. \par
Second, as the magnitude of lambda becomes bigger, the magnitude of $W_{ridge}$ become smaller. \par
The first observation is not often the cases. But the second observation can be explained that as the regularizer $\lambda$ become bigger, the $W$ is regularized, so that it is smaller. \par
By comparing Table~\ref{tab:Ridge_Regression} and Table~\ref{tab:Linear_Regression}, we can see that, the performance and the weight magnitude is almost the same as the $\lambda$ is small, but the difference become larger as $\lambda$ grows. \par
We also explore the weight mantitude between LR and RR under different $\lambda$ magnitude setting. Specifically, we set $log_{10}^{\lambda}$ in range from -7 to 3. We can see from Fig~\ref{fig:ridge_w}, as the magnitude of $\lambda$ growing, the weight magnitude of ridge regression become much smaller than linear regression. \par
\begin{table}[!hbt]
	% Center the table
	\begin{center}
		% Title of the table
		\caption{Different lambdas' impact in terms of error and $W$ magnitude. Best result are in bold.}
		\label{tab:Ridge_Regression}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|c|c|c|c|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			$log_{10}^{\lambda}$ & -2 & -1 & 0 & 1 & 2 & 3 \\
			\hline
			$MSE_{train}$   & \textbf{10.23} & \textbf{10.23} & 10.24 & 10.63 & 30.37 & 181.35   \\
			\hline
			$MSE_{val}$  & \textbf{17.08} & 17.09 & 17.16 & 18.20 & 43.92 & 214.55   \\
			\hline
			$L_2norm(W_{ridge})$  & 0.83 & 0.82 & 0.81 & 0.72 & 0.50 & 0.38 \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\begin{table}[!hbt]
	% Center the table
	\begin{center}
		% Title of the table
		\caption{Linear Regression Error and $W$ magnitude.}
		\label{tab:Linear_Regression}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|}
			% To create a horizontal line, type \hline
			\hline
			$MSE_{train}$ & 10.23    \\
			\hline
			$MSE_{val}$ & 17.08    \\
			\hline
			$L_2norm(W)$ & 0.83  \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{ridge_w}
		% Create a subtitle for the figure.
		\caption{The magnitude of $W_{ridge}$ under different lambda mgnitude.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:ridge_w}
	\end{center}
\end{figure}

\subsection{Gradient Descent, Stochastic Gradient Descent and Mini Batch Gradient Descent}
In this section, we conduct experiments on optimizing the LR model by using GD, SGD, MBGD  algorrithms, and compare them in terms of convergence and time cost. \par
We first evaluate the convergence of three algorithms, specificlly we set batch size in a range from 1 to number of full examples in training set. When the batch size is one, mini batch gradient descent becomes stochastic gradient descent and when the batch size equals to number of full examples, mini batch gradient descent becomes gradient descent. All experiments are with the same learning rate 0.01.\par
As we can see from Fig~\ref{fig:batch_size_train} and Fig~\ref{fig:batch_size_val}, as the batch size become larger, the convergence of the linear regression model bocome slower. The reason is that, in each epoch, the smaller the batch size, the model have more update steps, so the convergence is faster. Especially, the stochastic gradient descent converges within 10 steps, while gradient descent requires nearly 400 steps, there is a 400x margin.\par
We then measure the time cost for each batch size. \par 
As illustrated in Fig~\ref{fig:time_cost}, the smaller the batch size, more time cost is required, because of the explicit for loop in the SGD and MBGD. Especially, the GD requires only about 1 seconds in one step, while SGD requires 60 seconds, there exist a 60x margin.  \par
% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{batch_size_train}
		% Create a subtitle for the figure.
		\caption{The $MSE$ of training set under different batch size.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:batch_size_train}
	\end{center}
\end{figure}

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{batch_size_val}
		% Create a subtitle for the figure.
		\caption{The $MSE$ of validation set under different batch size.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:batch_size_val}
	\end{center}
\end{figure}

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{time_cost}
		% Create a subtitle for the figure.
		\caption{The time cost of 100 epoches under different batch size.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:time_cost}
	\end{center}
\end{figure}

\subsection{Impact of learning rate}
In this section, we evaluate the impact of learning rate in MBGD, we set batch size to 64 and epochs to 200. We set learning rate in a range e.g. 1e-4, 1e-3, 1e-2, 1e-1, 1. \par
As presented in Fig~\ref{fig:lr_train} and Fig~\ref{fig:lr_val}, small learning rate tends to make the convergence smoothly, but needs more epoches to fully converge. However, big learning rate make the convergence very fast, but will not guarateee that the convergence will be near the optimal(or local optimal) and makes the $MSE$ shaking around after a specific epoch.  \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{lr_train}
		% Create a subtitle for the figure.
		\caption{The $MSE$ in training set under different learning rate.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:lr_train}
	\end{center}
\end{figure}

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{lr_val}
		% Create a subtitle for the figure.
		\caption{The $MSE$ in validation set under different learning rate.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:lr_val}
	\end{center}
\end{figure}

\subsection{Weight magnitude between CSF and MBGD}
In this section, we explore the weight magnitude($L_2norm$) between CSF and MBGD optimized weight of linear regression. \par

Then, we experiments on comparing the weight magnitude of CFS and MBGD optimized LR. In MBGD, we set learning rate to 0.01 and batch size to 64. We can see that MBGD optimized LR's weight magnitude is stable after some epoches. But MBGD optimized weight's magnitude has a large margin(e.g. about 0.6) to CFS optimized weight. The reason is still unclear. \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{mbgd_w}
		% Create a subtitle for the figure.
		\caption{The magnitude of $W_{mbgd}$ under different epoches..}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:mbgd_w}
	\end{center}
\end{figure}

\subsection{Performance} 
In this section, we report the performance on CFS optimized LR, RR and MBGD optimized LR in training set, validation set and test set. The $\lambda$ is set to 1e-7 after validation. And batch size is set to 64 in MBGD, learing rate set to 0.01 and epoch set to 200 by validation. \par
From Table~\ref{tab:Performance}, we can see that alougth MBGD optimized LR's $MSE_{train}$ and $MSE_{val}$ are not the best, but its result in $MSE_{test}$ is outstanding. The reason remains unclear, maybe the same reason that the magnitude between CFS optimized LR and MBGD optimized LR has a large margin. \par
\begin{table}[!hbt]
	% Center the table
	\begin{center}
		% Title of the table
		\caption{Final Performance of CFS optimized LR, RR and MBGD optimized LR, best result are in bold.}
		\label{tab:Performance}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			& LR & RR & MBGD \\
			\hline
			$MSE_{train}$   & \textbf{10.23} & \textbf{10.23} & 11.37   \\
			\hline
			$MSE_{val}$  & \textbf{17.08} & \textbf{17.08} & 19.04   \\
			\hline
			$MSE_{test}$  & 10.20 &  10.20 & \textbf{10.14}  \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

>>>>

\usepackage{subfigure} % Written by Steven Douglas Cochran
                        % This package makes it easy to put subfigures
                        % in your figures. i.e., "figure 1a and 1b"
                        % Docs are in "Using Imported Graphics in LaTeX2e"
                        % by Keith Reckdahl which also documents the graphicx
                        % package (see above). subfigure.sty is already
                        % installed on most LaTeX systems. The latest version
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/subfigure/

@@

% Write abstract here
\begin{abstract}
In this report, we solve the binary classification problem in a9a dataset by Logistic Regression (LR) and Support Vector Machine (SVM). \\
We perform experiments on four aspects: \\
1. Hyper-parameter tuning in SVM. \\
2. Loss function comparision in SVM. \\
3. Initilizer comparision in both LR and SVM. \\
4. Optimizer comparision in both LR and SVM. \\
\end{abstract}

@@

% Main Part
\section{Methods and Theory}
In this part, we first define logistic regression and LR's loss function Binary Cross Entrophy (BCE). Then we define SVM and SVM's loss function Hinge Loss (HL).
\subsection{Logistic Regression}
Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \{0, 1\}$. Mathematically, for a single training datapoint $(x, y)$, LR assumes: \par
 \begin{center}
	\begin{equation}
	P(Y = 1|X = x) = \sigma(z) 
	\end{equation}
	\begin{equation}
	P(Y = 0|X = x) = 1 - \sigma(z)
	\end{equation}
	\begin{equation}
	z = F(x; W)
	\end{equation}
\end{center} \par
where $F(x; W)$ is linear regression parameterized by $W$ and $\sigma(.)$ is sigmoid function, where $\sigma(z) = \frac{1}{1 + e^{-z}} \in (0, 1)$.
\subsection{Binary Cross Entrophy}
Logistic regression assumes that each datapoint is independent, so the likelihood of all data is: \par
\begin{equation}
	\begin{aligned}
	L(W) &= \prod_{i=1}^m P(Y = y_i | X = x_i) \\ &= \prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} )
	\end{aligned}
\end{equation} \par

So our goal is to maximize the likelihood of data, in practice we maximize the log likelihood. \par
\begin{equation}
\begin{aligned}
LL(W) &= log\prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} ) \\ &= \Sigma_{i=1}^{m} (y_i \sigma(z) + (1 - y_i)(1 - \sigma(z)))
\end{aligned}
\end{equation} \par
When using mini batch gradient descent (MBGD) algorithm, we want to minimize something, so we minimize the negative log likelihood. \par

\begin{equation}
\label{eqa: NLL}
NLL(W) = -\Sigma_{i=1}^{m} (y_i \sigma(z) + (1 - y_i)(1 - \sigma(z)))
\end{equation} \par
Equation~\ref{eqa: NLL} is also called binary cross entropy.

\subsection{SVM and Hinge Loss}
Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \{-1, 1\}$. SVM is based on linear regression. When given a data point, it wants: \par

\begin{equation}
\label{eqa:svm_two}
\left\{
\begin{array}{lr}
w^{T}x + b \geq 1,~&if~y = 1  \\
w^{T}x + b \leq -1,~&if~y = -1 \\
\end{array}
\right.
\end{equation} \par
Equation~\ref{eqa:svm_two} can also be written to:
\begin{equation}
	y(w^{T}x + b) \geq 1
\end{equation} \par
Other than make the classification correct, SVM also wants to make the classification boundary as safe as possible. To achieve that, it wants to make the margin between the positive class and negative class as large as possible. \par
The positive boundary of SVM is $w^Tx + b = 1$ and negative boundary of SVM is $w^Tx + b = -1$. So the margin between this two boundary is: \par
\begin{equation}
	\label{eqa:margin}
	Margin = \frac{2}{||w||}
\end{equation} \par
In practice, instead of maximize Equation~\ref{eqa:margin}, we want to minimize: \par
\begin{equation}
	\frac{w^Tw}{2}
\end{equation} \par
So, the optimization problem for SVM is:
\begin{equation}
	\begin{aligned}
	\label{eqa:svm_optimization}
	min_{w, b}~&\frac{w^Tw}{2} \\
	s.t.~&y_i(w^Tx_i + b) \geq 1, i=1, 2, ..., m
	\end{aligned}	
\end{equation} \par

Moreover, data point may not be linearly separable. Even the data point is linear separable, the outliers in dataset will hurt the performance of SVM. So, SVM introduce slack variable $\xi_i $ for each data point, which represents how much data point $i$ is on the wrong side of margin boundary. \par
1. if $\xi_i = 0$, it is ok. \par
2. if $ 0 < \xi_i < 1 $, the data point is correctly classified, but with a smaller margin than $\frac{1}{||w||}$. \par
3. if $\xi_i > 1$, the data point is incorrectly classified. \par
Then the optimization problem becomes: 
\begin{equation}
	\begin{aligned}
	\label{eqa:svm_soft_optimization}
	min_{w, b}~&\frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \xi_i \\
	s.t.~&y_i(w^Tx_i + b) \geq 1 - \xi_i, i=1, 2, ..., m
	\end{aligned}	
\end{equation} \par
As $ \xi_i \geq 1 - y_i(w^Tx_i + b), i=1, 2, ..., m$, so
\begin{equation}
\label{eqa:xi}
\xi_i = 
\left\{
\begin{array}{lr}
	1 - y_i(w^{T}x_i + b),&if~1 - y_i(w^{T}x_i + b) \geq 0  \\
	0,&if~1 - y_i(w^{T}x_i + b) < 0  \\
\end{array}
\right.
\end{equation} \par
So \par
\begin{equation}
	\label{eqa:hinge_loss}
	\xi_i = max(0, 1 - y_i(w^Tx_i + b))
\end{equation} \par
Equation~\ref{eqa:hinge_loss} is the Hinge Loss (HL). Finally the optimization problem for SVM becomes
\begin{equation}
\label{eqa:svm_final_optimization}
min_{w, b}~\frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))
\end{equation} \par
We do a small modification for Equation~\ref{eqa:svm_final_optimization}, so that we can see the role of $C$ in SVM.
\begin{equation}
	\begin{aligned}
	min_{w, b}~\lambda w^Tw + \frac{1}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b)) \\
	where~\lambda = \frac{1}{2C}
	\end{aligned}
\end{equation} \par
Here, we can see that $\lambda$ e.g. $\frac{1}{2C}$ is the regularizer, like Ridge Regression (RR). So, the magnitude of $W$ is in direct proportion to $C$.

\section{Experiments}
\subsection{Dataset}
We conduct all the experiments on a9a dataset, which has total 48842 examples and each example's form is $(x, y)$, where $x \in \mathbf{R}^{123}$ and $y \in \{0, 1\}~(in~LR)~and~\{-1, +1\}~(in~SVM)$. We split the dataset into three part: 26049 training examples, 6512 validation examples and 16281 test examples. We normalized the $X_{train}, X_{val}, X_{test} $ by using the mean and variance of $X_{train}$.

\subsection{Implementation}
We implement the LR, SVM, optimizers, initilizers and loss functions using python and mainly rely on the numpy package.

\subsection{Hyper-parameter C in SVM}
In this section, we explore the influence of C in SVM. We set $log_{10}^{C}$ in a coarse-grained range e.g. -2, -1, 0, 1, 2, 3, 4, and compare $loss_{train}$, $loss_{val}$, $accuracy_{train}$, $accuracy_{train}$ and $l_2norm$ of $w$, where $loss =  \frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))$ and $ l_2norm(w) = \sqrt{\Sigma_{i=1}^n w_i}$. We zero initilize $w$ and $b$, use SGD as optimizer with learning rate 0.001, set epoch to 200 and batch size to 64. \par
From Fig~\ref{fig:C_loss}, we can see that, when $C$ is very small, e.g. smaller than 1, the gradient descent process is very unstable and the loss is higher than other. As $C$ goes up, the loss decreases, e.g. from 1 to 10. But when $C$ gets larger than 10, the loss become slightly bigger, but still better than small $C$, like 0.01 and 0.1. So, we can draw the conclusion that, bigger $C$ usually better than small $C$, and the best C is in the middle, which is not very big but also not very small. As we can see from Fig~\ref{fig:C_loss}, $C = 10$ gets the lowest loss.   \par
From Fig~\ref{fig:C_acc}, we can see that, when $C$ is very small, e.g. 0.01, the accracy in both training set and validation set is much lower than others. Small $C$ like 0.01 and 0.1 get worse performance comparing with others. In training set, the accracy is very similar when $C$ bigger than 1. In validation set, $C = 10$ gets slightly better performance comparing with others. Best validation performance under each $C$ setting can be found in Table~\ref{tab:C_performance}. \par
From Fig~\ref{fig:c_mag}, we can see that, as $C$ goes up, $l_2norm(w)$ goes up except $C = 100$. As said above, $\frac{1}{2C}$ can be viewed as regurilizer, so when $C$ is bigger, the smaller of its impact on regurization, so the weight maginitude goes up. 
\begin{figure*}[!hbt]
	\centering
	\subfigure[$Loss_{train}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_train_loss}}
	\subfigure[$Loss_{val}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_val_loss}}
	\caption{ $Loss_{train}~and~Loss_{val}$ under different $C$. }
	\centering
	\label{fig:C_loss}
\end{figure*} \par

\begin{figure*}[!hbt]
	\centering
	\subfigure[$Accuracy_{train}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_train_acc}}
	\subfigure[$Accuracy_{val}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_val_acc}}
	\caption{ $Accuracy_{train}~and~Accuracy_{val}$ under different $C$. }
	\centering
	\label{fig:C_acc}
\end{figure*} \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{c_magnitude}
		% Create a subtitle for the figure.
		\caption{The magnitude of $W$ under different $C$.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:c_mag}
	\end{center}
\end{figure} \par

\begin{table}[!hbt]
	% Center the table
	\begin{center}
		% Title of the table
		\caption{Best Result in Validation set under different C's settings. Best result are in bold.}
		\label{tab:C_performance}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|c|c|c|c|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			$log_{10}^{C}$ & -2 & -1 & 0 & 1 & 2 & 3 & 3 \\
			\hline
			$Accuracy_{val}$   & 84.39 & 84.42 & 84.72 & \textbf{84.75} & 84.73 & 84.56 & 84.49   \\
			\hline
			$Epoch$  & \textbf{2} & 86 & 62 & 138 & 173 & 147 & 145   \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\subsection{Loss function comparision in SVM}
In this section, we conduct experiment on loss function comparision in SVM. Especially, we compare two loss function, hinge loss which is illustrated above And Exponential Loss (EL), where $EL = exp\{-y_i(w^Tx_i + b)\}$. More formaly, $HL(z) = max(0, 1 - z)$ and $EL(z) = exp^{-z}$. Fig~\ref{fig:loss_fn} shows that HL and EL both have one advantage and one disadvantage. HL is stable when z is very mall, however EL become very large, which will lead to numeric unstable. EL is derivable every but HL is not derivable when $z = 1$. We use SGD as optimizer with learning rate 0.001, set epoch to 200, batch size to 64 and C to 10.\par
From Fig~\ref{fig:l_val_loss} and Fig~\ref{fig:l_val_acc}, we can see that the performance of HL is superior. EL has numeric unstablity problem during gradient descent process. \par
\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{loss_fn}
		% Create a subtitle for the figure.
		\caption{The plot of HL and EL.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:loss_fn}
	\end{center}
\end{figure} \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{l_val_loss}
		% Create a subtitle for the figure.
		\caption{$loss_{val}$ under different loss function.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:l_val_loss}
	\end{center}
\end{figure} \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{l_val_acc}
		% Create a subtitle for the figure.
		\caption{$Accuracy_{val}$ under different loss function.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:l_val_acc}
	\end{center}
\end{figure} \par

\subsection{Initilizer comparision in both LR and SVM}
In this section, we compare the performance of LR and SVM under different initilizers. We explore over ones, zeros, xavier uniform and random initializer. Ones initilizers makes the initial $w$ to all one and Zeros initilizers makes the initial $w$ to all zero. Xavier uniform initializer uniformally initial $w$, but bounded to interval $[-n, n]$, where $n$ is $W$'s dimension. Random initializer initial $w$ from standard normal distribution. We use SGD as optimizer with learning rate 0.001, set epoch to 200, batch size to 64 and C to 10 in SVM. We use HL as SVM's loss function and BCE as LR's loss function.\par
From Fig~\ref{fig:lr_init_val_loss} and Fig~\ref{fig:lr_init_val_acc}, we can see that LR's performance is affected by the initilizer. Typically Ones initilizer brings the worst performance and Xavier uniform initializer bring the best performance. \par
From Fig~\ref{fig:svm_init_val_loss} and Fig~\ref{fig:svm_init_val_acc}, we can see that SVM is very robust to the initilizer, different initilizer didn't disturb the performance. \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{lr_init_val_loss}
		% Create a subtitle for the figure.
		\caption{LR's $BCE_{val}$ under different initilizer.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:lr_init_val_loss}
	\end{center}
\end{figure} \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{lr_init_val_acc}
		% Create a subtitle for the figure.
		\caption{LR's $Accuracy_{val}$ under different initilizer.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:lr_init_val_acc}
	\end{center}
\end{figure} \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{svm_init_val_loss}
		% Create a subtitle for the figure.
		\caption{SVM's $HL_{val}$ under different initilizer.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:svm_init_val_loss}
	\end{center}
\end{figure} \par

\begin{figure}[!hbt]
	% Center the figure.
	\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{svm_init_val_acc}
		% Create a subtitle for the figure.
		\caption{SVM's $Accuracy_{val}$ under different initilizer.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:svm_init_val_acc}
	\end{center}
\end{figure} \par
